Language-Based Security for Low-Level MPC

### 2024-08-18 csf25/main.tex
checkpoint

\documentclass[acmsmall,screen,review]{acmart} % 1-column
%\documentclass[sigconf]{acmart} % 2-column

\usepackage{amsmath}
\usepackage{amstext}
\usepackage{fp-frame}
\usepackage[latin1]{inputenc}
\usepackage{mathpartir}
\usepackage{fancyvrb}
\usepackage{moreverb}
\usepackage{stmaryrd}
\usepackage{enumerate}
\usepackage{thmtools,thm-restate}
\usepackage{comment}
\usepackage{booktabs,array}
\usepackage{rotating}
\usepackage{xcolor}

\input{macros}
\input{figures}

\setcopyright{none}

@@

\title{Language-Based Security for Low-Level MPC}

\author{Christian Skalka}
\affiliation{
  \institution{University of Vermont}
  \city{}
  \country{}
%  \city{Burlington}
%  \country{USA}
}
\email{ceskalka@uvm.edu}

\author{Joseph P. Near}
\affiliation{
  \institution{University of Vermont}
  \city{}
  \country{}
%  \city{Burlington}
%  \country{USA}
}
\email{jnear@uvm.edu}

\begin{abstract}
  Secure Multi-Party Computation (MPC) is an important
  enabling technology for data privacy in modern distributed
  applications. Currently, proof methods for low-level MPC protocols
  are primarily manual and thus tedious and error-prone, and are also
  non-standardized and unfamiliar to most PL theorists. As a step
  towards better language support and language-based enforcement, we
  develop a new staged PL for defining a variety of low-level
  probabilistic MPC protocols. We also formulate a collection of
  confidentiality and integrity hyperproperties for our language model
  that are familiar from information flow, including conditional
  noninterference, gradual release, and robust declassification. We
  demonstrate their relation to standard MPC threat models of passive
  and malicious security, and how they can be leveraged in security
  verification of protocols. To prove these properties we develop
  automated tactics in $\mathbb{F}_2$ that can be integrated with
  separation logic-style reasoning.
\end{abstract}

\begin{comment}
%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10002978.10002986.10002990</concept_id>
       <concept_desc>Security and privacy~Logic and verification</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10003752.10003753.10003757</concept_id>
       <concept_desc>Theory of computation~Probabilistic computation</concept_desc>
       <concept_significance>300</concept_significance>
       </concept>
   <concept>
       <concept_id>10003752.10003790.10003806</concept_id>
       <concept_desc>Theory of computation~Programming logic</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Security and privacy~Logic and verification}
\ccsdesc[500]{Theory of computation~Probabilistic computation}
\ccsdesc[500]{Theory of computation~Programming logic}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Secure multiparty computation, security verification, probabilistic programming, programming languages, information flow.}
\end{comment}

\settopmatter{printfolios=true}
%\maketitle

%\input{intro}

%\input{lang}

%\input{minitypes}

\input{scratch}

%\input{model}

%\input{hyper}

%\input{bruteforce}

%\input{metalang}

%\input{example-gmw}

%\input{example-bdoz}

%\input{conclusion}

\bibliographystyle{ACM-Reference-Format}
\bibliography{logic-bibliography,secure-computation-bibliography}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.

\usepackage{amsmath}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage{fp-frame}
\usepackage[latin1]{inputenc}
\usepackage{mathpartir}
\usepackage{fancyvrb}
\usepackage{moreverb}
\usepackage{stmaryrd}
\usepackage{enumerate}
\usepackage{thmtools,thm-restate}
\usepackage{comment}
\usepackage{booktabs,array}
\usepackage{rotating}
\usepackage{xcolor}

\input{macros}
%\input{figures}

@@

\input{lang}

\input{smt}

\input{ctj}

\input{itj}

\input{metalang}

\input{examples}

\bibliographystyle{IEEEtran}
\bibliography{logic-bibliography,secure-computation-bibliography}
